---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r setup, include=TRUE}
library(reticulate)
#, engine.path="/anaconda3/bin/python"
use_python("/anaconda3/bin/python")
library(readr)
library(dplyr)
library(ggplot2)
```


This notebook tests out the [reticulate](https://rstudio.github.io/reticulate/) package.  First, make sure that the development version is installed.  Next, make sure that the python engine that you prefer is the one being used.  The code for this step is usually hidden in a setup code chunk.  The setup code chink for this notebook is shown at the very top of this page.


```{r}
DATA_PATH_CEP<-"/Users/thomasallen/cep_ob3b/data"
DATA_PATH_CEP_PHOT<-paste(DATA_PATH_CEP,"/Photometry",sep="")
DATA_PATH<-"/Users/thomasallen/cep_ob3b/cepr/data/"
```


```{bash}

which python

```

```{python}

import sys as sys

print(sys.version)
print(sys.path)

pvar = 7 + 3

print(pvar)

```

```{r}
py$pvar
```


```{python}
print("New Chunk")
print(pvar)
```


In the process we will also use `bash` code chunks to examine what data we have.  And take a look at the first few lines of one of the data files.
```{bash}


cd /Users/thomasallen/cep_ob3b/data/Photometry
head CH1phot.dat
```

