---
title: "Spectral Typing"
output:
  pdf_document: default
  html_document:
    df_print: paged
#bibliography: cep_ob3b_spectroscopy.bib
---


Here we will take a look at the spectral typing of stars toward Cep OB3b.   

![image](../graphs/irac1_obs.pdf)

```{r setup, include=TRUE}
#devtools::install_github("rstudio/reticulate")
library(reticulate)
use_python("/anaconda3/bin/python")
library(readr)
library(dplyr)
library(ggplot2)
source("/Users/thomasallen/cep_ob3b/cepr/lib/helpers.R")

#library('ProjectTemplate')
#project_directory<-"/Users/thomasallen/cep_ob3b/cepr"
#setwd(project_directory)
#load.project()
```


```{python}

import sys as sys
sys.path.append("/Users/thomasallen/Code/python_scripts/Functions")

```



```{python}
import sys as sys
sys.path.append("/Users/thomasallen/Code/python_scripts/Functions")

from hecto_funcs import hectospec_fits_open_index
from astropy.io import ascii

import numpy as np
import matplotlib.pyplot as plt

dir_in='/Users/thomasallen/cep_ob3b/data/Spectroscopy/'
standards_fn=dir_in+'spec_standards.dat'
#print(standards_fn)
stand=ascii.read(standards_fn)
spt=stand['col1']
fn=stand['col2']
num=stand['col3']

off = np.arange(len(fn))

#print(fn)
#print('Off')
#print(off)


#psize=16
#fsize=22
#fsize2=24
#fig = plt.figure(figsize=(10,15))
#plt.gcf().subplots_adjust(bottom=0.15,left=0.15)
#plt.subplot(1,1,1)
#plt.ylim=[0,100]
#plt.xlabel(r"Wavelength ($\mu \mathrm{m}$)",fontsize=fsize2)
#
#plt.show()

```


We read in the data set.  Here we will start with the `full.df.csv` dataset.  For details about this data set see the [data documentation]().  We are interested in the spectral typing of the stars with *Hectospec* spectra.  

```{r}
data_path <- "/Users/thomasallen/cep_ob3b/cepr/data/"
data_path2 <- "/Users/thomasallen/cep_ob3b/data/"

#full.df.csv

full.df <- read_csv(paste(data_path2,"full.df.csv",sep=""))

#head(full.df)
gsdss.df <- read_csv(paste(data_path,"gsdss.csv",sep=""))
rsdss.df <- read_csv(paste(data_path,"rsdss.csv",sep=""))

full.df <- full.df %>% 
    mutate(gmag=gsdss.df$mag,gerr=gsdss.df$err) %>% 
    mutate(rmag=rsdss.df$mag,rerr=rsdss.df$err)

full.df <- full.df %>% 
    mutate(bmag=as.numeric(bmag)) %>% 
    mutate(berr=as.numeric(berr)) %>%
    mutate(vmag=as.numeric(vmag)) %>% 
    mutate(verr=as.numeric(verr)) %>% 
    mutate(imag=as.numeric(imag)) %>% 
    mutate(ierr=as.numeric(ierr)) 

```

We want the objects that have spectral types.  These will be rows where the columns `spt`, the spectral type as classified by eye, and `spt_old`, the spectral type as classified by regression.  

Lets make a column that tells us which stars we classified as probable background giants.

```{r}


full.df <- full.df %>% 
    mutate(giant = ifelse(cagiant == "giant" | nagiant == "giant", "giant", "unclassified"))


spt.df <- full.df %>% 
    filter(is.na(spt)==FALSE & is.na(spt_old)==FALSE)
    

head(spt.df)


plot1 <- spt.df %>% ggplot(aes(x=spt_old,y=spt,color=giant)) +
    geom_point()


plot1
```

It looks like many of the stars classified as K5/K6 background giants have the wrong spectral classification.


Lets look at the distibution of visually determined spectral types of these "background giants".

```{r}

spt.df %>% 
    filter(giant=="giant") %>% 
    ggplot(aes(x=spt,fill=member)) + geom_bar()

```

Ok, so after removing potential members, there are about 25 K5/K6 stars that still remain, and over 20 K7s.




```{r}

ext_cc_plot_fit <- function(df,c1=vmag,c2=jmag,c3=kmag,xtitle="J - K",ytitle="V - J")  {
    
    # Plots X - J vs. J - K and fits a linear model 
    # Slope of linear model is used to derive Ax/Aj extinction coefficient
    
    c1<-enquo(c1)
    c2<-enquo(c2)
    c3<-enquo(c3)
    
    df.plot <- df %>% 
        filter(giant=="giant") %>% 
        filter(member=="non-member") %>% 
        filter(is.na(!!c2)==FALSE & is.na(!!c3)==FALSE & is.na(!!c1)==FALSE) %>% 
        filter(spt==65 | spt==66) %>% # | spt==67) 
    

        #mutate(c1=as.numeric(c1)) %>%
        mutate(x=!!c2 - !!c3,y= !!c1 - !!c2) %>% 
        select(x,y)  
    #filter(jmk < 1.75)

   
    plot <- df.plot %>% 
        ggplot(aes(x=x,y=y)) +
        geom_point() +
        geom_smooth(method='lm') +
        labs(x=xtitle,y=ytitle)



    fit <- lm(y ~ x, data = df.plot)
    print(summary(fit))
    #print(plot)
    
    return(plot)
  #  
}
```


```{r}
# g - J

spt.df %>% ext_cc_plot_fit(c1=gmag,ytitle="g - J")

```

```{r}
# V - J

spt.df %>% ext_cc_plot_fit(c1=vmag,ytitle="V - J")

```
```{r}
# V - J 
# Filter outlier

spt.df %>%
    filter(jmag - kmag < 1.75) %>% 
    ext_cc_plot_fit(c1=vmag,ytitle="V - J")

```

```{r}
# r - J

spt.df %>% ext_cc_plot_fit(c1=rmag,ytitle="r- J")
```


```{r}


alam <- function(slope) {
    
    alam <- slope * (1 - 0.397) + 1
    
    return(alam)
    
}

alam(4.3)

alam(3.5)

alam(2.6)



```

