---
title: "Cep OB3b Data"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(reticulate)
library(readr)
library(dplyr)
library(ggplot2)
```


This page details the data input and wrangling process for the Cep OB3b data set.  The data come from a variatey of sources that I collected/compiled throughout my Ph.D. work.  

I am currently using directories filled with text files for both data and indices.  A tidy format would be preferred to countless index arrays.

This data has a long history.  It originates with data from the *Spitzer* Young Stellar Cluster Survey, and additional *Spitzer* missions.  This accounts for the $3.6 - 24~\mu m$ data.  The X-ray data is from a proposal I helped lead the year before I entered graduate school.  Much of the ramaining data, including the *Hectospec* and *Hectochelle* spectroscopy, was collected while I was a graduate student. It is supplemented by data from other researchers and programs such as $2MASS$. These sources will be acknowledged throughout this document and in a bibliography(**PUT BIBLIOGRAPHY LINK** ).

Over the years I went from using Interactive Data Language (IDL) to python to a mixture of R and Python.  

## Photometry

First let's consider the photometry data.  

```{r}
DATA_PATH_CEP<-"/Users/thomasallen/cep_ob3b/data/"
DATA_PATH_CEP_PHOT<-paste(DATA_PATH_CEP,"Photometry/",sep="")
DATA_PATH<-"/Users/thomasallen/cep_ob3b/cepr/data/"
```
Let's take a look at some of the data that provided the foundation for this project.  *Spitzer* band 1 (I may also use the term channel interchangabley with band).  This band is in the mid-infrared part of the spectrum with a central wavelength of $\sim [3.6]~\mu m$.(**PUT LINK TO SPITZER INFO**)

I previously wrote a number of Python scripts to help me work with this data and I don't want that time to have been wasted.  Fortunately, R Markdown allows use of Python code chunks. Unfortunately, it does not seem as if the chunks can communicate with each other.  L'll just deal for now.  If anyone knows a better way, please let me know.

```{bash}

which python

```

```{python, engine.path="/anaconda3/bin/python"}

import sys as sys

print(sys.version)
print(sys.path)


```

In the process we will also use `bash` code chunks to examine what data we have.  And take a look at the first few lines of one of the data files.
```{bash}


cd /Users/thomasallen/cep_ob3b/data/Photometry
ls
head CH1phot.dat
```
As we can see from the peak into the Ch 1 data we have space delimited columns, there not labeled but the first column is magnitude and the second is error.  We also have a header line that gives us the wavelength and the IDL save file source.

It also tells us that values of `-100.00000` and `10.000000` are being used to indicate missing magnitude and error data, respectively. 

```{python, engine.path="/anaconda3/bin/python"}
import sys as sys
from astropy.io import ascii
import numpy as np
import os as os
sys.path.append("/Users/thomasallen/python_scripts/Functions")

from cep_funcs import get_cep_phot,write_cep_phot_csv,get_cep_spec,get_cep_index_sav
import csv

#Paths to Data
dir_text_data='/Users/thomasallen/cep_ob3b/data/Photometry/'
dir_csv_data="/Users/thomasallen/cep_ob3b/cepr/data/"

# Change directory to data origin
os.chdir(dir_text_data)

band="Vphot"

print('Loading V-band')
mag,err = get_cep_phot(band)

print(mag)

write_cep_phot_csv(mag,err,filename=band+'.csv',dir_write=dir_csv_data)

```
I'm not sure this is the most efficient way.  R can read in text files. Let's use the `readr` package (Note: this, and all, packages are loaded in the first R chunk used to set-up the environment).  

In the process we will also use `bash` code chunks to examine what data we have.  And take a look at the first few lines of one of the data files.

Here we can test if the above python code worked.
```{bash}


cd /Users/thomasallen/cep_ob3b/cepr/data
ls
head Vphot.csv
```

Let's load this into R using the `readr` package.

```{r}

vphot.df<-read_csv(paste(DATA_PATH,"Vphot.csv",sep=""))

```
And maybe a function to check for non-NaN's, aka, real numbers.
```{r}

count_real <- function(df) {
    
    df %>% 
        mutate(real=(is.na(mag)==0)) %>% 
        group_by(real) %>% summarise(n=n())
    
}

count_real(vphot.df)
```


I was going to use `read_delim` but was having issues with the whitespace.  So I chose a solution that involved writing to `.csv` in python.
```{r eval=FALSE}
fn <- paste(DATA_PATH_PHOT,"CH1phot.dat",sep="")

ch1_phot <- read_delim(fn,delim=" ",col_types=list(col_character()),col_names=c("phot"),skip=1)
ch1_phot

nn<-nrow(ch1_phot)

mag <- vector(mode="numeric",length=nrow(ch1_phot))
err <- vector(mode="numeric",length=nrow(ch1_phot))


#for (ii in 1:nrow(ch1_phot)) {
#    
#    #print(ii)
#    strsplit(as.character(ch1_phot[ii])," ")
#    #tmp<-strsplit(as.character(ch1_phot[ii])," ")
#    #mag[ii]<-tmp[1]
#    #err[ii]<-tmp[2]
#    
#}
print(mag)
```

Now lets write a loop in python to write the photometric data we want to `.csv` files in my `R ProjectTemplate` `data` directory.
```{python, engine.path="/anaconda3/bin/python", eval=FALSE}
import sys as sys
from astropy.io import ascii
import numpy as np
import os as os
sys.path.append("/Users/thomasallen/python_scripts/Functions")

from cep_funcs import get_cep_phot,write_cep_phot_csv,get_cep_spec,get_cep_index_sav
import csv

#Paths to Data
dir_text_data='/Users/thomasallen/cep_ob3b/data/Photometry/'
dir_csv_data="/Users/thomasallen/cep_ob3b/cepr/data/"

# Change directory to data origin
os.chdir(dir_text_data)

file_list=["Bphot",
    "CH1phot",
    "CH2phot",
    "CH3phot",
    "CH4phot",
    "Haphot",
    "Hphot",
    "Iphot",
    "Jphot",
    "Kphot",
    "MIPSphot",
    "Rphot",
    "Vphot",
    "gbell",
    "gsdss",
    "ibell",
    "isdss",
    "rbell",
    "rsdss",
    "ubell",
    "usdss",
    "zbell",
    "zsdss"]


for file in file_list:

    mag,err = get_cep_phot(file)
    write_cep_phot_csv(mag,err,filename=file+'.csv',dir_write="/Users/thomasallen/cep_ob3b/cepr/data/")

```

Now let's check the directory and see if the files are there.
```{bash}

cd /Users/thomasallen/cep_ob3b/cepr/data/
ls
```

There they are.

## Astrometry

